CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability

### 2019-02-15 gpus/paper.tex
minor

Discuss OpenMP, OpenACC, and CUDA.

@@

@@

\software{MPICH, GCC, Castro, python, matplotlib}

\acknowledgements \castro\ is freely available at
\url{http://github.com/AMReX-Astro/Castro}.  The work at Stony Brook
was supported by DOE/Office of Nuclear Physics grant DE-FG02-87ER40317
and NSF award AST-1211563.  An award of computer time was provided by
the Innovative and Novel Computational Impact on Theory and Experiment
(INCITE) program.  This research used resources of the Oak Ridge
Leadership Computing Facility at the Oak Ridge National Laboratory,
which is supported by the Office of Science of the U.S. Department of
Energy under Contract No. DE-AC05-00OR22725.  We thank NVIDIA Corporation
for the donation of a Titan X Pascal used in this research.

>>>>

@@

\subsection{Offloading to GPUs}

CUDA Fortran is not as well supported as CUDA C/C++.  In particular,
CUDA Fortran does not automatically create both the host and device
kernel, necessitating one to do this themselves.  Usually this means
having two copies of a source routine, one marked up with device
attributes.  Keeping them in sync essentially requires that this
action be scripted, but in our experience, this scripting is fragile
because of the need to deal with Fortran syntax, preprocessor
directives, ...  Thus the pure CUDA route for the compute kernels makes the most sense
with C/C++ kernels, and not Fortran kernels.

OpenACC

OpenMP

\subsection{Example of advancing a grid}

@@

\software{MPICH, GCC, Castro, AMReX, python, matplotlib}

\facilities{OLCF, NERSC}

\acknowledgements \castro\ is freely available at
\url{http://github.com/AMReX-Astro/Castro}.  The work at Stony Brook
was supported by DOE/Office of Nuclear Physics grant DE-FG02-87ER40317
and NSF award AST-1211563.  An award of computer time was provided by
the Innovative and Novel Computational Impact on Theory and Experiment
(INCITE) program.  This research used resources of the Oak Ridge
Leadership Computing Facility at the Oak Ridge National Laboratory,
which is supported by the Office of Science of the U.S. Department of
Energy under Contract No. DE-AC05-00OR22725.  We thank NVIDIA Corporation
for the donation of a Titan X Pascal and Titan V used in this research.
